%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Ryota B. Seki}
\address{Honolulu, HI, 96813}
\contacts{(808) 281-4228 \linebreak ryotabs@hawaii.edu \linebreak https://github.com/ryotabs}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Web Application Developer}{University of Hawaii at Manoa}{December 2019 - December 2021}
			UH Groupings			
			\begin{itemize}
				\item Implemented major UX feature that allows a group administrator to select and remove multiple group members from a web interface.
				\item Created a brand new mentoring program while transitioning to remote work to streamline and ease on-boarding of new hires.
				\item Contributed technical documentation to improve onboarding and developer experience.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{IT Help Desk Student Assistant}{University of Hawaii at Manoa}{Aug 2019 - Dec 2019}		
			\begin{itemize}
				\item Performed IT troubleshooting over the phone and over email for all 8 University of Hawaii campuses. 
				\item Promoted to Student Tech, resolving IT issues in-person for staff and faculty members on the UH Manoa campus.
				\item Utilized effective communication skills to recommend best practices for consumer hardware/software use.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Client Systems Technician}{Hawaii Air National Guard}{March 2014 - March 2020}
			\begin{itemize}
				\item Provided 24/7 computer, networking, and server hardware/software support for over 400 personnel. 
				\item Upgraded over 300 systems during massive Windows 10 overhaul.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Honolulu, HI}{University of Hawaii at Manoa }{August 2017 -- December 2021}
			\begin{itemize}
				\item B.S. in Computer Science
				\item Undergraduate Coursework: Operating Systems; Databases; Algorithms; Calculus II; Data Science; Software Engineering I, II; Network Science and Methodology; Machine Level Programming; Program Structure.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{UH Groupings} (2019 - 2021) High traffic full-stack web application that allows group management of members in the UH system. Utilized SpringBoot stack with J2EE, Maven, Tomcat, RestAPI, AngularJS, JUnit.
				\item \textbf{Green Loan Portal} (2019) A web portal for the HGIA that simplifies the Green Loan application process and writes the inputted information to their PDF application form. Meteor stack with React, SemanticUI, Node.js, MongoDB.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Miscellaneous}{}{}
			\begin{itemize}
				\item Linux operating systems and command line. Installed a Linux operating system with terminal and Linux command line utilities to learn file directory structure, Linux packages and utilities, and command line.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Java/J2EE; Python
				\item Vim; Git/Github; Bash Terminal; React; AngularJS; Node.js; SpringBoot
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
