%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Ryota Seki}
\address{Honolulu, HI, 96813}
\contacts{(808) 281-4228 \linebreak ryotabs@hawaii.edu \linebreak https://github.com/ryotabs}

\begin{document}

	% Print the header
	\makeheader

	\begin{cvsection}{Professional Experience}
		\begin{cvsubsection}{Full Stack Developer}{eWorld Enterprise Solutions}{Feburary 2022 - Present}
			PHIMS
			\begin{itemize}
				\item Provided maintenence and bugfixes for a vital State of Hawaii web application.
			\end{itemize}
		\end{cvsubsection}
		
	\end{cvsection}

	% Print the content
	\begin{cvsection}{Internship Experience}
		\begin{cvsubsection}{Web Developer}{University of Hawaii}{December 2019 - December 2021}
			UH Groupings
			\begin{itemize}
				\item Collaborated with senior team member to implement major UX feature that allows a group administrator to select and remove multiple group members from a web interface.
				\item Created several API features that reduced the amount of repeated code to significantly increase code quality coverage.
				\item Created a brand new mentoring program while transitioning to remote work to streamline and ease on-boarding of new hires. Personally mentored 3 new developers.
				\item Contributed technical documentation to improve onboarding and developer experience.
			\end{itemize}
		\end{cvsubsection}
		
	\end{cvsection}
		
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{UH Groupings} (2019 - 2021) High traffic full-stack web application that allows group management of members in the UH system. Utilized SpringBoot stack with AngularJS, Boostrap/JQuery front-end, J2EE/Java backend, REST API, and JUnit and Jasmine testing framework.
				\item \textbf{Green Loan Portal} (2019) A web portal for the HGIA that simplifies the Green Loan application process and writes the inputted information to their PDF application form. Full-stack application using the Meteor stack with React, SemanticUI, Node.js, MongoDB.
				\item \textbf{Mozilla Profiler} (2022) A development tool for Mozilla firefox that visualizes performance for web browsers. Rewrote testing to mock fetch and response data.
				\item \textbf{PHIMS} (2022 - present) A web application for the State of Hawaii Department of Transportation Harbors Division that allows the harbor master to document inbound and outbound vessels. Used the Spring stack with Vue.js and Oracle database.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Java/J2EE; Javascript, HTML/CSS
				\item Git; React; AngularJS; Node.js; MongoDB; Oracle Database
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Education}
		\begin{cvsubsection}{Honolulu, HI}{University of Hawaii at Manoa }{August 2017 -- December 2021}
			\begin{itemize}
				\item Bachelor's of Science in Computer Science
				\item Coursework: Databases(SQL); Algorithms; Data Science/Analytics; Software Engineering I, II; Network Science and Methodology; Machine Level Programming; Program Structure (C and Unix programming).
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Mentorship Experience}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Math Tutor, University of Hawaii, 2017
				\item Mentored 3 new hires with a mentorship program I created from scratch during my internship
				\item Military experience; Mentored 5 junior subordinates at home station from 2014 - 2020
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	
\end{document}
