%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Ryota Seki}
\address{Honolulu, HI, 96813}
\contacts{(808) 281-4228 \linebreak ryotabs@hawaii.edu}

\begin{document}

	% Print the header
	\makeheader

	\begin{cvsection}{Professional Experience}
		\begin{cvsubsection}{System Analyst / Developer}{eWorld Enterprise Solutions}{Feburary 2022 - Present}
			\textbf{Port Hawaii Information Management System}
			\begin{itemize}
				\item Implemented efficient debugging with the use of JUnit tests and standard practices to improve troubleshooting speed by 20\%.
				\item Designed and developed over 10 front-end and back-end features in Java and Javascript by collaborating with business analysts and senior engineers.
				\item Perform occasional deploys on Jenkins to verify that features are working in Production build.
			\end{itemize}
			\textbf{Department of Transportation - Highways Division Project Status Sheets (PSS)}
			\begin{itemize}
				\item Produced over 10 Jasper reports to remove project blocker and enabled a 2-year project to close-out/end.
				\item Mentored/managed 1 developer interns to provide professional and techincal feedback.
				\item Particiapte in bi-weekly client meetings to ensure scope of requirements were still being fulfilled. 
			\end{itemize}
			\textbf{State of Hawaii Disability Compensation Division - Interim Forms Portal}
			\begin{itemize}
				\item Implemented a user interface that allows a user to upload forms in Vue.js from scrach in an urgent timeframe.
				\item Implemented automated email functionality that sends confirmation email upon successful form upload.
				\item Utilized Google Cloud Platform to write various backend functions.
			\end{itemize}
		\end{cvsubsection}
	\begin{cvsubsection}{Web Application Developer}{University of Hawaii}{December 2019 - December 2021}
			\textbf{UH Groupings}
			\begin{itemize}
				\item Collaborated with senior team member to implement major UX feature that allows a group administrator to select and remove multiple group members from a web interface.
				\item Created several API features that reduced the amount of repeated code to significantly increase code quality coverage.
				\item Created a brand new mentoring program while transitioning to remote work to streamline and ease on-boarding of new hires. Personally mentored 3 new developers.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
		
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Port Hawaii Information Management System} Full-stack web application that allows management of Harbors assets in the State of Hawaii. Java backend w/ SpringBoot, Oracle SQL database, VueJS frontend used with Jenkins for deployment.
				\item \textbf{Highways - Project Status Sheets} Full-stack web application developed for the Department of Transportation Highways Divison for the State of Hawaii that allows users to print reports of various construction project statuses. Java backend with SQL database, VueJS frontend and Jasper Reports for report printing functionality.
				\item \textbf{UH Groupings} (Associated with Univeristy of Hawaii) High traffic full-stack web application that allows group management of members in the UH system. Utilized SpringBoot stack with AngularJS, Boostrap/JQuery front-end, J2EE/Java backend, REST API, and JUnit and Jasmine testing framework.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Java/J2EE; Javascript
				\item Git; Spring/SpringBoot; React; AngularJS; Vue.js; Node.js; SQL; Google Cloud (GCP); Bash
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Education}
		\begin{cvsubsection}{Honolulu, HI}{University of Hawaii at Manoa }{August 2017 -- December 2021}
			\begin{itemize}
				\item Bachelor's of Science in Computer Science
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	
\end{document}
